---
title: "My Fancy Presentation"
author: "Leo Peng"
date: "3/12/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide

Plain Text

*italicized text*

**bold text**

`for (i %in% 1:10)`


***
A Slide without a title

## My Title
### A Top Level Subheading
#### A Second Level Subheading

- Bullet 1
- Bullet 2

1. Item 1
2. Item 2

```{r, echo=T, eval=F}
head(mtcars)
```

## My Plot Slide

```{r, echo=F, fig.align="center", fig.cap="My Awesome Figure"}
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="MPG")
```



## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

